### 2014-04-22 brains-protocol.tex
Remove BCs in correlation and variation plots (/!\ but not yet in timebag evolution plots)

\begin{figure}[!th]
    \centering
    \includegraphics[width=0.788\linewidth]{images/computed-figures/feature_correlations-filter2.png}
    \caption{Spearman correlations in the filtered set of features \rk{further remove FA betweenness?}}
    \label{fig:feature-corrs-filtered}
\end{figure}

>>>>

\begin{figure}[!th]
    \centering
    \includegraphics[width=0.6975\linewidth]{images/computed-figures/feature_correlations-filter2.png}
    \caption{Spearman correlations in the filtered set of features}
    \label{fig:feature-corrs-filtered}
\end{figure}
